---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# mobile-app

<!-- badges: start -->
<!-- badges: end -->

this repo has scripts to prepare the data for the EUROCONTROL Data mobile app.

## PocketHost API

We have 2 applications hosted at [PocketHost][https:://pockethost.io]

1. https://eurocontrol-data.pockethost.io
1. https://eurocontrol-data-test.pockethost.io

The first as "production" the other as testing instance.

These applications have various collections (behind the scenes they are SQLite tables)
that are exposed as REST API.
The package `pockethostr` is (partially) wrapping the REST API to allow CRUD
operations as detailed below.

The API covers
* (public) List/Search: listing of (subset of) collection records
* (public) View: viewing of all details of one record of the collection
* (admin only) Create: create a new record
* (admin only) Update: update an existing record
* (admin only) Delete: delete an existing record

Admin-only operations need authentication.

In the following sections we provide examples for the above operations for the
network data collection, `nw_traffic`.

We start with loading some helper packages...

```{r setup, eval=TRUE, warning=FALSE, message=FALSE}
library(pockethostr)
library(lubridate)
library(dplyr)
library(purrr)
library(readxl)
library(stringr)
library(magrittr)

app_main <- "eurocontrol-data"
app_test <- "eurocontrol-data-test"
collection <- "nw_traffic"
```


### List/Search

This example shows how to retrieve the second page (5 per page instead of the
default 30) entries.
Records are returned in reverse order with respect to the `FLIGHT_DATE` property.

```{r list-search, eval=TRUE}
ph_list_records(
  app = app_test,
  api = "/api/collections/",
  collection = collection,
  # fields = "FLIGHT_DATE,DAY_TFC,Y2D_TFC_YEAR",
  perPage = 5,
  page = 2,
  sort = "-FLIGHT_DATE")
```

Eventually you can add a (server side) filter and pick only some columns:

```{r list-search-filter, eval=TRUE}
ph_list_records(
  app = app_test,
  api = "/api/collections/",
  collection = collection,
  fields = "id,FLIGHT_DATE,DAY_TFC,Y2D_TFC_YEAR",
  filter ="('2024-01-05'<=FLIGHT_DATE&&FLIGHT_DATE<'2024-01-15')", 
  sort = "-FLIGHT_DATE") |> 
  dplyr::relocate(id, .before = DAY_TFC)
```

### View

NOT IMPLEMENTED YET

```{r view}
# TBD
```


### Authentication

For admin only operations you need to pass a token, hence you need to be authenticated.

```{r authenticate, eval=FALSE}
username <- "performancereviewunit@gmail.com"
password <- "you know it"

# authenticate over test app
adm_test <- ph_authenticate_admin_username_password(
  app_test,
  "/api/admins/auth-with-password",
  username,
  password)

# authenticate over main app
adm_main <- ph_authenticate_admin_username_password(
  app_main,
  "/api/admins/auth-with-password",
  username,
  password)
```


### Create record(s)

Let's get some internal data

```{r examples, eval=FALSE}

today <- (lubridate::now() +  days(-1)) |> format("%Y%m%d")
base_dir <- '//sky.corp.eurocontrol.int/DFSRoot/Groups/HQ/dgof-pru/Data/DataProcessing/Covid19/Archive/'
base_file <- '99_Traffic_Landing_Page_dataset_new_{today}.xlsx'
archive_dir <- '//sky.corp.eurocontrol.int/DFSRoot/Groups/HQ/dgof-pru/Data/DataProcessing/Covid19/Archive/web_daily_json_files/app/'
last_day <-  (lubridate::now() +  days(-1))
last_year <- as.numeric(format(last_day,'%Y'))

nw_traffic_data <-  read_xlsx(
  path  = fs::path_abs(
    str_glue(base_file),
    start = base_dir),
  sheet = "NM_Daily_Traffic_All",
  range = cell_limits(c(2, 1), c(NA, 39))) |> 
  as_tibble()

nw_traffic_last_day <- nw_traffic_data %>%
  filter(FLIGHT_DATE == max(LAST_DATA_DAY))

nw_traffic_latest <- nw_traffic_last_day %>%
  select(
    FLIGHT_DATE,
    DAY_TFC,
    DAY_DIFF_PREV_YEAR_PERC,
    DAY_TFC_DIFF_2019_PERC,
    AVG_ROLLING_WEEK,
    DIF_WEEK_PREV_YEAR_PERC,
    DIF_ROLLING_WEEK_2019_PERC,
    Y2D_TFC_YEAR,
    Y2D_AVG_TFC_YEAR,
    Y2D_DIFF_PREV_YEAR_PERC,
    Y2D_DIFF_2019_PERC
  ) |> 
  as.list() |> 
  purrr::list_transpose() |> 
  magrittr::extract2(1)
```

Then we create a new record in the two apps.

```{r create-record, eval=FALSE}

# create latest record on test
ph_create_record(
  app = app_test,
  api = "/api/collections",
  collection = collection,
  token = adm_main$token,
  body = nw_traffic_latest)

# create latest record on main
ph_create_record(
  app = app_main,
  api = "/api/collections",
  collection = collection,
  token = adm_main$token,
  body = nw_traffic_latest)
```


Here just a sort of batch

```{r create-many, eval=FALSE}
# data for 2024
lol <- nw_traffic_data |> 
  filter(FLIGHT_DATE < today()) |> 
  select(
    FLIGHT_DATE,
    DAY_TFC,
    DAY_DIFF_PREV_YEAR_PERC,
    DAY_TFC_DIFF_2019_PERC,
    AVG_ROLLING_WEEK,
    DIF_WEEK_PREV_YEAR_PERC,
    DIF_ROLLING_WEEK_2019_PERC,
    Y2D_TFC_YEAR,
    Y2D_AVG_TFC_YEAR,
    Y2D_DIFF_PREV_YEAR_PERC,
    Y2D_DIFF_2019_PERC
  ) |> 
  as.list() |> 
  purrr::list_transpose()


#------------- TEST ------------
for (r in lol) {
  # print(r)
  ph_create_record(
    app = app_test,
    api = "/api/collections",
    collection = collection,
    token = adm_test$token,
    body = r)
  Sys.sleep(0.1)
}


# delete all records in test
lor <- ph_list_records(
  app = app_test,
  api = "/api/collections/",
  collection = collection,
  sort = "-FLIGHT_DATE")

ids <- lor |> pull(id)
for (i in ids) {
  ph_delete_record(
    app = app_test,
    api = "/api/collections",
    collection = collection,
    token = adm_test$token,
    id = i)
  Sys.sleep(0.3)
}

```

### DELETE all

```{r delete-all, eval=FALSE}
#------------- TEST ------------
# delete all records in test (just one page)
lor <- ph_list_records(
  app = app_test,
  api = "/api/collections/",
  collection = collection,
  sort = "-FLIGHT_DATE")

ids <- lor |> pull(id)
for (i in ids) {
  ph_delete_record(
    app = app_test,
    api = "/api/collections",
    collection = collection,
    token = adm_test$token,
    id = i)
  Sys.sleep(0.1)
}



```

